PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd

>>>>

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

```

```{r NMSW sum score frequencies}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.sum_score)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.sum_score) %>%
  mutate(Prop = round(n/sum(n), 2))
```
